Post-replication citation patterns in psychology: Four case studies

### 2021-02-06 manuscript/manuscript.Rmd
turned off tidylog

```{r load_packages, warning=F}
# load packages
library(knitr) # for literate programming
library(papaja) # for article template
library(tidyverse) # for data munging
library(tidylog) # inline tidyverse feedback
library(here) # for finding files
library(ggpubr) # for arranging plots
library(kableExtra) # for table formatting
```

>>>>

```{r load_packages, warning=F}
# load packages
library(knitr) # for literate programming
library(papaja) # for article template
library(tidyverse) # for data munging
library(here) # for finding files
library(ggpubr) # for arranging plots
library(kableExtra) # for table formatting
```
